Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-16 hscc2017/paper.tex
wording

\subsection{Program Synthesis for the Example}
%
We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  
Assuming a precision of $I_p=16$, $F_p=24$,  
we start with an a-priori candidate solution with all coefficients zero (note that the controller is in the FWL domain, hence we use $\tilde{C}(z)$): 
%
$$ 
\tilde{C}(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
$$
In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:
%
$$ 
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}. 
$$
%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$ 
We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
phase, where we obtain the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\tilde{C}(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
$$ 
This time, the {\sc uncertainty} check does not find any
counterexample and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the set of counterexamples.  Back in the {\sc synthesize}
phase, we re-start the process with a candidate solution with all
coefficients $0$, as above.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$ 
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}. 
$$
In the {\sc synthesize} phase, we get a new candidate solution that
eliminates the new, higher precision counterexample:
%
$$ 
\tilde{C}(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

@@

The first set of benchmarks uses the discrete model $G_1(z)$ of a cruise control

@@

The second set of benchmarks considers the discrete model $G_2(z)$ 

@@

A third set of benchmarks uses the discrete model $G_{3}(z)$ for satellite attitude 

@@

The fourth set of benchmarks presents an alternative discrete model $G_4(z)$ 

@@

%\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined

@@

The seventh set of benchmarks contains a well-studied discrete  
non-minimal phase model $G_{7}(z)$. As known, non-minimal phase model offers 
additional difficulties for the design of stable controllers~\cite{Doyle:1991:FCT:574259}. 

@@

The eighth set of benchmarks describes the discrete model $G_{8}(z)$ for the \textit{Helicopter Longitudinal Motion},
which provides the longitudinal motion dynamics of a helicopter~\cite{Franklin15}. 

@@

The ninth  set of benchmarks contains the discrete model $G_{9}(z)$ for the known \textit{Inverted Pendulum}, which 
describes a pendulum dynamics with its center of mass above its pivot point~\cite{Franklin15}. 

@@

The tenth set of benchmarks contains the \textit{Magnetic Suspension} discrete model $G_{10}(z)$, which describes the dynamics of a mass that levitates with support only of a magnetic field~\cite{Franklin15}. 

@@

The eleventh set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{11}(z)$, which 
describes a system to read and write data on a storage device~\cite{Franklin15}.

@@

The last set of benchmarks considers a discrete model $G_{12}(z)$ 
that is typically used for evaluating stability
margins and controller fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.

Additional benchmarks were created for the \textit{Cruise Control System}, \textit{Spring-mass damper}, and \textit{Satellite} considering parametric additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in Eq.~\eqref{digital_plant_tf}). The uncertainties are deviations bounded to a maximum magnitude of $0.5$ in each coefficient. These uncertain models are respectively represented by $G_{1b}(z)$, $G_{2b}(z)$, $G_{3b}(z)$, and $G_{3d}(z)$.

>>>>

\subsection{Program Synthesis for the Example}
%
We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  Assuming a precision of $I_p=16$,
$F_p=24$, we start with an a-priori candidate solution with all coefficients
zero (the controller performs FWL arithmetic, hence we use
$\tilde{C}(z)$):
%
$$ 
\tilde{C}(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
$$
In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:
%
$$ 
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}. 
$$
%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$ 
We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
phase, where we obtain the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\tilde{C}(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
$$ 
This time, the {\sc uncertainty} check does not find any
counterexample and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the set of counterexamples.  Back in the {\sc synthesize}
phase, we re-start the process with a candidate solution with all
coefficients $0$, as above.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$ 
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}. 
$$
In the {\sc synthesize} phase, we get a new candidate solution that
eliminates the new, higher precision counterexample:
%
$$ 
\tilde{C}(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

@@

The first set of benchmarks uses the discrete model $G_1$ of a cruise control

@@

The second set of benchmarks considers the discrete model $G_2$ 

@@

A third set of benchmarks uses the discrete model $G_{3}$ for satellite attitude 

@@

The fourth set of benchmarks presents an alternative discrete model $G_4$ 

@@

%\noindent We can obtain $G_{4}$ using the ZOH discretization defined

@@

The seventh set of benchmarks contains a well-studied discrete non-minimal
phase model $G_{7}$.  Non-minimal phase models cause additional
difficulties for the design of stable
controllers~\cite{Doyle:1991:FCT:574259}.

@@

The eighth set of benchmarks describes the discrete model $G_{8}$ for the
\textit{Helicopter Longitudinal Motion}, which provides the longitudinal
motion dynamics of a helicopter~\cite{Franklin15}.

@@

The ninth set of benchmarks contains the discrete model $G_{9}$ for the
known \textit{Inverted Pendulum}, which describes a pendulum dynamics with
its center of mass above its pivot point~\cite{Franklin15}.

@@

The tenth set of benchmarks contains the \textit{Magnetic Suspension}
discrete model $G_{10}$, which describes the dynamics of a mass that
levitates with support only of a magnetic field~\cite{Franklin15}.

@@

The eleventh set of benchmarks contains the \textit{Computer Tape Driver}
discrete model $G_{11}$, which describes a system to read and write data
on a storage device~\cite{Franklin15}.

@@

The last set of benchmarks considers a discrete model $G_{12}$ that is
typically used for evaluating stability margins and controller
fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.

Additional benchmarks were created for the \textit{Cruise Control System},
\textit{Spring-mass damper}, and \textit{Satellite} considering parametric
additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in
Eq.~\eqref{digital_plant_tf}).  The uncertainties are deviations bounded to
a maximum magnitude of $0.5$ in each coefficient.  These uncertain models
are respectively represented by $G_{1b}$, $G_{2b}$, $G_{3b}$ and
$G_{3d}$.
